First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-01-24 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
edit the main latex file
writing the results section

A DVCS process on a nuclear target differ from single nucleon scattering in 
providing access to the measure two DVCS channels. In the coherent DVCS 
channel, the target nucleus ($A$) remains intact and recoils as a whole while 
emitting a real photon ($eA \rightarrow e' A' \gamma$), allowing to measure the 
nuclear GPDs of the target. In the incoherent channel, the nucleus breaks up 
and the DVCS takes place on a bound nucleon ($N$) that emits the final photon 
($eA \rightarrow e' N' \gamma$ X), enabling the GPDs measurement of the bound 
nucleons and to study their modifications in the nuclear medium via the GPDs.  
Figure \ref{fig:diags} illustrates the dominant mechanism for the coherent DVCS 
channel on $^4$He. At sufficiently large squared electron momentum transfer 
$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ ($= 
(p-p')^{2}$), the QCD factorization theorem predicts that the DVCS handbag 
diagram can be factorized into two parts, hard and soft parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
interaction and it is calculable through perturbative methods, while the 
soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron. Experimentally, the DVCS reaction is 
indistinguishable from the Bethe-Heitler (BH) process, which is the reaction 
where the final photon is emitted either from the incoming or the outgoing 
leptons. The BH process is not sensitive to GPDs and does not carry information 
about the partonic structure of the hadronic target. The BH cross section is 
calculable from the well-known electromagnetic form factors.

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\vspace{-0.cm}
\caption{Deep virtual Compton scattering process in the handbag approximation.}
\label{fig:diags}
\end{figure}

@@

@@

The experiment, CLAS-EG6, took place in the experimental Hall-B of Jefferson 
laboratory (JLab) in 2009. JLab delivers, simultaneously, a nearly 100\% duty 
factor polarized electrons into three experimental Halls (A, B, C). The data 
were collected over three months via projecting a 6.064 GeV longitudinally 
polarized beam, (83$\%$ polarization), on a 6 atm gaseous $^4$He target.  The 
Hall-B Large Acceptance Spectrometer (CLAS) basic design \cite{CLAS_ref} was 
upgraded, during the CLAS-E1DVCS1 experimental run \cite{Girod:2007aa} in 2005, 
with a specially designed electromagnetic calorimeter, Inner calorimeter (IC).  
The IC has extended the photon detection acceptance of CLAS, which is 
originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle reach as minimum 
as 4$^{\circ}$. During the same experiment, a 5 Tesla solenoid was added around 
the target to shield the inner detectors from the low-energy M\o ller 
electrons.

@@

\begin{figure}[tb]
\includegraphics[width=7.0cm,angle=-90]{figs/RTPC.pdf}
\vspace{-0.9cm}
\caption{Left: A picture of the CLAS-EG6 RTPC before insertion into the 
   solenoid. Right: A cross section of the CLAS-EG6 RTPC perpendicular to the 
beam direction. An illustration of a $^4$He track originating from the 
pressurized straw target is shown along with the electrons produced in the 
drift region.}
\label{fig:RTPC}
\end{figure}

%DVCS selection
Identifying the coherent DVCS candidates is the first step of the data 
analysis. These events have one electron, one $^4$He, and at least one photon 
in the final state. Electrons were identified by passing the fiducial cuts and 
having signals in all the sub-detectors of CLAS spectrometer (drift chambers, 
Cherenkov counters, the standard CLAS electromagnetic calorimeter, and 
scintillators). $^4$He tracks were identified by passing all the geometrical, 
timing and quality cuts in the RTPC detector. The most energetic IC photon was 
considered as the DVCS photon candidate. Next, a $Q^{2}>1~[GeV^{2}/c^{2}]$ cut 
is applied on the DVCS candidates in order to ensure that the interaction 
occurs at the partonic level and the applicability of the factorization in the 
DVCS handbag diagram. Once the three final state particles were identified with 
their 3-momentum vectors, the exclusivity of the coherent DVCS events were 
ensured by applied a set of 3$\sigma$ exclusivity cuts. The exclusive cuts are: 
the co-planarity angle ($\Delta \phi$), missing energy, missing mass squared 
and missing transverse momentum in the $e'~^4He'~\gamma~X$ final state 
configuration, the missing mass squared in the $e'~^4He'~X$ and $e'~\gamma~X$ 
configurations, and finally the cone angle ($\theta$) between the measured real 
photon and the missing particle in the $e'~^4He'~X$ configuration.  
Figure~\ref{fig:kin-cuts} presents four of the applied exclusivity cuts.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the seven coherent DVCS exclusivity cuts. The black 
distributions represent the coherent DVCS events candidate. The shaded 
distributions represent the events which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent $3\sigma$ cuts. The 
distributions from left to right and from top to bottoms are: $\Delta \phi$, 
missing energy and missing mass squared in $e'~^4He'~\gamma~X$, and the cone 
angle ($\theta$) between the measured and the calculated final state real 
photon.}
\label{fig:kin-cuts}
\end{figure}
After all the particle identification requirements on the individual particle 
of the coherent DVCS events and after all the exclusivity cuts, we ended up 
with about 3500 events. Figure \ref{fig:kin-coverage} presents the 
($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$) kinematic coverage of the collected DVCS 
events.

@@

%asymmetries
Even with all the previously presented exclusive cuts, the selected events are
not all true DVCS events. We identified several background contributions to the 
coherent DVCS process, in particular accidental events and exclusive Deeply 
Virtual $\pi^0$ Production (DV$\pi^0$P). The accidental events where the 
different particles come from different events are suppressed by the limited 
phase space allowed by the exclusivity cuts. We estimate the accidental events 
to represent 4.1\% of our sample. This relatively large number is due to the 
small cross section of the DVCS. We evaluated this contribution by selecting 
events passing all our cuts but with particles originating from different 
vertices. Regarding the DV$\pi^0$P, which can easily be mistaken with DVCS when 
one of the two photons of the $\pi^0$ decay is produced at low energy in the 
laboratory frame. To estimate the importance of this background, we developed 
an event generator that we calibrated to match our measured experimental yield 
of exclusive $\pi^0$. We used this generator together with a GEANT3 simulation 
of our detection system to estimate the ratio of acceptance between DV$\pi^0$P 
where the two photons are detected and those where only one photon is detected 
and would pass our DVCS selection cuts. This ratio obtained from simulation is 
then multiplied by the measured yield of DV$\pi^0$P events, indicating a 
contamination of 2 to 4\%. The study of systematics errors showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%). However added quadratically, these errors sum up to 
10\% which remain for all bins well below the statistical errors.

The beam-spin asymmetry is our DVCS observable, which is measurable using a 
polarized lepton beam on an unpolarized target (U). It is convenient to use the 
beam-spin asymmetry as a DVCS observable because most of the experimental 
normalization and acceptance issues cancel out in the asymmetry ratio. It is 
defined in terms of the cross sections as:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
  where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross 
  section for a positive (negative) beam helicity. $A_{LU}$ can be simplified 
  in terms of the collected number of events in each beam-helicity state 
  ($N^{+}$, $N^{-}$) as:
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
of events detected with positive and negative electron helicity, respectively.  
The statistical uncertainty of $A_{LU}$ is
\begin{equation}
   \sigma_{A_{LU}} = \frac{1}{P_{B}} \sqrt{ \frac{1 - (P_{B}A_{LU})^{2}}{N}}
\end{equation}
where $N (N^{+} + N^{-}) $ is the total number of measured events.

%CFF
we extract the GPD $H$ in a model independent way (figure~\ref{fig:CFF_HA}).  
This is possible using the beam-spin asymmetry ($A_{LU}$) expression for 
spin-zero target at leading twist \cite{Kirchner:2003wt,Belitsky:2008bz}:
\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. The 
$\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the 
nuclear form factor $F_A$ and the independent variables $Q^2$, $x_{B}$ and $t$.  
These factors are simplified as:
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize

Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor. Their explicit expressions can be found in .

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$ in
   $Q^{2}$(top panel), $x_{B}$ (middle panel), and $-t$ (bottom panel) bins.  
   The error bars represent the statistical and the systematic uncertainties 
   added quadratically, shown on top in green are error bars representing only 
   the statistical uncertainties. The brown bands represent the systematic
uncertainties, including the normalisation systematic uncertainties. The red
curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
\vspace{-0.9cm}
\caption{}
\label{fig:alu90}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/Coherent_CFF.pdf}
\vspace{-0.9cm}
\caption{The model-independent extraction of the imaginary (blue points) and
real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
\label{fig:CFF_HA}
\end{figure}

@@

@@

>>>>

A DVCS process on a nuclear target differ from single nucleon scattering in 
providing access to the measure two DVCS channels. In the coherent DVCS 
channel, the target nucleus ($A$) remains intact and recoils as a whole while 
emitting a real photon ($eA \rightarrow e' A' \gamma$), allowing to measure the 
nuclear GPDs of the target. In the incoherent channel, the nucleus breaks up 
and the DVCS takes place on a bound nucleon ($N$) that emits the final photon 
($eA \rightarrow e' N' \gamma$ X), enabling the GPDs measurement of the bound 
nucleons and to study their modifications in the nuclear medium via the GPDs.  
Figure \ref{fig:diags} illustrates the dominant mechanism for the coherent DVCS 
channel on $^4$He. At sufficiently large squared electron momentum transfer 
$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ ($= 
(p-p')^{2}$), the QCD factorization theorem predicts that the DVCS handbag 
diagram can be factorized into two parts, hard and soft parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
interaction and it is calculable through perturbative methods, while the 
soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron.  
\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\vspace{-0.cm}
\caption{Deep virtual Compton scattering process in the handbag approximation.}
\label{fig:diags}
\end{figure}

@@

This work presents the first exclusive measurement of the beam-spin asymmetry 
of the reaction $e~^{4}He\rightarrow e'~^{4}He~\gamma$.This DVCS sensitive 
observable is measurable using a polarized lepton beam on an unpolarized target 
(U). It is convenient to use the beam-spin asymmetry as a DVCS observable 
because most of the experimental normalization and acceptance issues cancel out 
in the asymmetry ratio. It is defined in terms of the cross sections as:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross 
section for a positive (negative) beam helicity. Experimentally, the DVCS 
reaction is indistinguishable from the Bethe-Heitler (BH) process, where the 
final photon is emitted either from the incoming or the outgoing leptons. The 
BH process is not sensitive to GPDs and does not carry information about the 
partonic structure of the hadronic target, and it's amplitude is calculable 
from the well-known electromagnetic form factors.

The photon-electroproduction cross section can be decomposed into a BH,
a DVCS, and an interference terms. At leading twist, the amplitudes of the 
three terms can be decomposed into a finite sum of Fourier harmonics, the 
so-called BMK formalism, as shown for the nucleon DVCS in 
\cite{Belitsky:2001ns} and for the spinless nuclei in 
\cite{Kirchner:2003wt,Belitsky:2008bz}. Therefore, the beam-spin asymmetry 
($A_{LU}$) with the two opposite helicities of a longitudinally-polarized 
electron beam (L) on a spin-zero target (U) can be written as:
\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$.  
The $\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the 
nuclear form factor ($F_{A}(t)$) and the independent variables $Q^2$, $x_{B}$ 
and $t$. These factors are simplified as:
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize

Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor. Their explicit expressions can be found in 
\cite{Belitsky:2008bz}. Therefore, Using the $\alpha_{i}$ factors, one can 
obtain in a totally model-independent way $\Im m(\mathcal{H}_{A})$ and $\Re 
e(\mathcal{H}_{A})$ from fitting the experimental $A_{LU}$ as a function of 
$\phi$, the azimuthal angle between the ($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) 
planes, for given values of $Q^2$, $x_{B}$, and $t$.

@@

The experiment, CLAS-EG6, took place in the experimental Hall-B of Jefferson 
laboratory (JLab) in 2009. JLab delivers, simultaneously, a nearly 100\% duty 
factor polarized electrons into three experimental Halls (A, B, C). The data 
were collected over three months via projecting a 6.064 GeV longitudinally 
polarized beam, (83$\%$ polarization), on a 6 atm gaseous $^4$He target.  The 
Hall-B Large Acceptance Spectrometer (CLAS) basic design \cite{CLAS_ref} was 
supplemented, during the CLAS-E1DVCS1 experimental run \cite{Girod:2007aa} in 
2005, with a specially designed electromagnetic calorimeter, Inner calorimeter 
(IC). The IC has extended the photon detection acceptance of CLAS, which is 
originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle reach as minimum 
as 4$^{\circ}$.  During the same experiment, a 5 Tesla solenoid was added 
around the target to shield the inner detectors from the low-energy M\o ller 
electrons.

@@

\begin{figure}[tb]
\includegraphics[width=7.0cm,angle=-90]{figs/RTPC.pdf}
\vspace{-1.1cm}
\caption{Left: A picture of the CLAS-EG6 RTPC before insertion into the 
   solenoid. Right: A cross section of the CLAS-EG6 RTPC perpendicular to the 
   beam direction. An illustration of a $^4$He track originating from the 
   pressurized straw target is shown along with the electrons produced in the 
drift region.}
\label{fig:RTPC}
\end{figure}

%DVCS selection
Identifying the coherent DVCS candidates is the first step of the data 
analysis. These events have one electron, one $^4$He, and at least one photon 
in the final state. Electrons were identified by passing the fiducial cuts and 
having signals in all the sub-detectors of CLAS spectrometer (drift chambers, 
Cherenkov counters, the standard CLAS electromagnetic calorimeter, and 
scintillators). $^4$He tracks were identified by passing all the geometrical, 
timing and quality cuts in the RTPC detector. The most energetic IC photon was 
considered as the DVCS photon candidate. Next, a $Q^{2}>1~[GeV^{2}/c^{2}]$ cut 
is applied on the DVCS candidates in order to ensure that the interaction 
occurs at the partonic level and the applicability of the factorization in the 
DVCS handbag diagram. Once the three final state particles were identified with 
their 3-momentum vectors, the exclusivity of the coherent DVCS events were 
ensured by applying a set of exclusive cuts, which are: the co-planarity angle 
($\Delta \phi$), missing energy, missing mass squared and missing transverse 
momentum in the $e'^4He'\gamma X$ final state configuration, the missing mass 
squared in the $e'^4He'X$ and $e'\gamma X$ configurations, and finally the cone 
angle ($\theta$) between the measured real photon and the missing particle in 
the $e'^4He'X$ configuration. Figure~\ref{fig:kin-cuts} presents four of the 
applied exclusivity cuts, where 3$\sigma$ cuts are applied on all the exclusive 
quantities except the missing energy, for which a [-0.45,0.5] GeV cut was 
adopted to reduce the background contribution.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the seven coherent DVCS exclusivity cuts. The black 
distributions represent the coherent DVCS events candidate. The shaded 
distributions represent the events which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied exclusivity 
cuts. The distributions from left to right and from top to bottoms are: $\Delta 
\phi$, missing energy and missing mass squared in $e'^4He'\gamma X$, and the 
cone angle ($\theta$) between the measured and the calculated photons.}
\label{fig:kin-cuts}
\end{figure}
After all the requirements on the individual final state particles of the 
coherent DVCS events and the exclusivity cuts, we ended up with about 3500 
events. Figure \ref{fig:kin-coverage} presents the ($Q^{2}$,$x_{B}$) and 
($Q^{2}$,$-t$) kinematic coverage of the collected DVCS events.

@@

%asymmetries
Even with all the previously presented exclusive cuts, the selected events are
not all true DVCS events. We identified several background contributions to the 
coherent DVCS process, in particular accidental events and exclusive Deeply 
Virtual $\pi^0$ Production (DV$\pi^0$P). The accidental events where the 
different particles come from different events are suppressed by the limited 
phase space allowed by the exclusivity cuts. We estimate the accidental events 
to represent 4.1\% of our sample. This relatively large number is due to the 
small cross section of the DVCS. We evaluated this contribution by selecting 
events passing all our cuts but with particles originating from different 
vertices. Regarding the DV$\pi^0$P, which can easily be mistaken with DVCS when 
one of the two photons of the $\pi^0$ decay is produced at low energy in the 
laboratory frame. To estimate the importance of this background, we developed 
an event generator that we calibrated to match our measured experimental yield 
of exclusive $\pi^0$. We used this generator together with a GEANT3 simulation 
of our detection system to estimate the ratio of acceptance between DV$\pi^0$P 
where the two photons are detected and those where only one photon is detected 
and would pass our DVCS selection cuts. This ratio obtained from simulation is 
then multiplied by the measured yield of DV$\pi^0$P events, indicating a 
contamination of 2 to 4\%. The study of systematics errors showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%). However added quadratically, these errors sum up to 
10\%, which remain for all bins well below the statistical errors.

$A_{LU}$ can be simplified in terms of the collected number of events in each 
beam-helicity state ($N^{+}$, $N^{-}$) as:
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
of DVCS events detected with positive and negative electron helicity with 
respect to the beam direction. The statistical uncertainty of $A_{LU}$ is
\begin{equation}
   \sigma_{A_{LU}} = \frac{1}{P_{B}} \sqrt{ \frac{1 - (P_{B}A_{LU})^{2}}{N}}
\end{equation}
where $N (N^{+} + N^{-}) $ is the total number of measured events.

Due to our limited statistics only, a two-dimensional binning is carried out in 
this work. The strongest dependence of $A_{LU}$ is on the azimuthal angle 
($\phi$). Thus, the coherent measured ranges of $Q^{2}$, $x_{B}$ and $t$ are 
binned statistically into three bins. Then, the identified DVCS events in each 
bin are binned into nine bins in $\phi$.  Therefore, we are left
with $Q^{2}$-$\phi$ bins integrated over the full ranges of $x_{B}$ and $t$, 
$x_{B}$-$\phi$ bins integrated over $Q^{2}$ and $t$, and $t$-$\phi$ bins 
integrated over $Q^{2}$ and $x_{B}$.

Figure \ref{fig:A_LU-coh} presents the coherent $A_{LU}$ for the three
sets of two-dimensional bins. The asymmetries are fitted with the form of
equation \ref{eq:A_LU-coh}, where the real and the imaginary part of the CFF
$\mathcal{H}_{A}$ are the free parameters in the fit. Figure \ref{fig:alu90} 
shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the fitted $A_{LU}$ signals 
at $\phi$~=~90$^{\circ}$. The $x_{B}$ and $-t$-dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}.  Their model relies on the impulse approximation and uses 
advanced spectral function of the nuclei to calculate the nuclear GPDs and then 
the observables. The calculations were carried out at slightly different 
kinematics than ours but provide already some guidance. The experimental 
results appear to have larger asymmetries compared to the calculations.  These 
differences may arise from nuclear effects which are not taken into account in 
the model, such as long-range interactions. Our measurements also agree with 
those of HERMES, considering their large uncertainties.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$ in
   $Q^{2}$(top panel), $x_{B}$ (middle panel), and $-t$ (bottom panel) bins.  
   The error bars represent the statistical and the systematic uncertainties 
   added quadratically, shown on top in green are error bars representing only 
   the statistical uncertainties. The bluish-gray bands represent the 
   systematic uncertainties, including the normalisation systematic 
uncertainties. The red curves represent fits in the form of equation 
\ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
   the coherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
   \cite{HERMES_BSA}, the colored curves represent theoretical calculations 
from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/Coherent_CFF.pdf}
\caption{The model-independent extraction of the imaginary (blue points) and
real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).  
The full red curves are calculations based on the impulse approximation from
\cite{Vadim_priv}. The black-dashed curves in the right plots are calculations 
from a convolution model based on the VGG model for the nucleons' GPDs 
\cite{Guidal_priv}. The blue long-dashed curve on the top-right plot is from
the off-shell calculations based on reference \cite{GonzalezHernandez:2012jv}.}
\label{fig:CFF_HA}
\end{figure}

@@

\bibitem{Belitsky:2001ns} A.~V.~Belitsky, D.~Mueller and A.~Kirchner,
     Nucl.\ Phys.\ B {\bf 629}, 323 (2002)

@@

\bibitem{simonetta_2}
   S.~Liuti and K.~Taneja, Phys.\ Rev.\ C {\bf 72}, 032201 (2005)

\bibitem{HERMES_BSA}
   A. Airapetian et al. (HERMES Collaboration), Phys.\ Rev.\ C {\bf 81}, 035202 
   (2010)

\bibitem{Vadim_priv}
   Private communications with V.~Guzey based on: 
   V.~Guzey, Phys.\ Rev.\ C {\bf 78}, 025211 (2008).

\bibitem{Guidal_priv}
   Private communications with M.~Guidal based on: M.~Guidal, M.~V.~Polyakov, 
   A.~V.~Radyushkin and M.~Vanderhaeghen, Phys.\ Rev.\ D {\bf 72}, 054013
   (2005).

\bibitem{GonzalezHernandez:2012jv} 
   Private communications with S.~Liuti based on: J.~O.~Gonzalez-Hernandez, 
   S.~Liuti, G.~R.~Goldstein and K.~Kathuria,
   Phys.\ Rev.\ C {\bf 88}, no. 6, 065206, (2013).
